Gradual Soundness: Lessons from Static Python

### 2021-12-11 pj-7.1/paper.tex
pj: reword first-class / mixin discussion

\SP{} does not attempt to type first-class classes:
partly because they see little use at Instagram (FILL how much?)
and partly because it is unclear how to incorporate them into
the nominal type system.
The straightforward but restrictive approach is to force code
that uses a first-class class to expect instances of a particular
static class.
FILL is the bracha cook mixin pattern a way to work within nominal~\cite{bc-oopsla-1990}?
Flatt et al.~\cite{fkf-popl-1998} propose a different method that accommodates mixins,
but the method calls a second layer of interface types.
Muehlboeck and Tate~\cite{mt-oopsla-2021} similarly allow structural objects with interfaces.
Adding these layers to \SP{} is an open question; in particular,
Python's multiple inheritance would complicate the mixin story.

@@

>>>>

\SP{} does not attempt to type first-class classes:
partly because they see little use at Instagram (FILL how much?)
and partly because it is unclear how to incorporate them into the
nominal type system.
The straightforward but restrictive approach is to force code that uses a
first-class class to expect subtypes of a particular named static class.
Flatt et al.~\cite{fkf-popl-1998} propose a more-flexible approach, %(specifically for mixins)
but it requires a second layer of \emph{interface types} atop the nominal hierarchy.
MonNom~\cite{mt-oopsla-2021} uses interfaces in a similar way to accommodate
structural objects.
Adding an interface layer to \SP{} is an open question.

% in particular , Python's multiple inheritance would complicate the mixin story.
% Classic mixins rely on structural types~\cite{bc-oopsla-1990}.

@@

%% https://github.com/facebookincubator/cinder/tree/cinder/3.8/Tools/benchmarks
%%
%% deltablue
%% fannkuch
%% nbody
%% nqueens
%% pystone
%% richards
%% richards_static
%%
%% UHOH except for richards_static, none of these have types!!!
%% Need to ask if C&D have other typed benchmarks around
%% ... if not, ask them to port these and measure and tune if needed.
